WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-03-22 article/Article.tex
Acknowledgments
darcs-hash:20060322120625-2fc9d-59b521f5fba2e29b528f9fb3c0fe4168840ff9f8.gz

\section{Acknowledgments}

>>>>

\section{Acknowledgments}
I thank Dr Pierre Adenot and all the {\em Embryon et Biotechnologie} team for their
patience during the long development time before getting a tool really usable.

I also thank Richard Beare for his early interest in using itk with python, and for
his useful feedbacks.

Thank to Charl P. Botha for is help to debug WrapITK on windows plateform and for the
patches he has contributed.

Finally, we thank the ITK developers for the great tool which is ITK, and for the
previous work done on wrapping system - without it WrapITK would not be there.
